---
title: "Weekly Assessment of CVP and SWP Delta Operations on ESA-listed Species"
author: "Bureau of Reclamation"
date: '2022-08-09'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(knitr)
library(tidyr)

library(readxl)
library(CDECRetrieve)
library(flextable)
```

```{r, echo = FALSE}
data_folder <- "data_report/"
```

# Executive Summary

# Operational and Regulatory Conditions

# Biology, Distribution, and Evaluation Winter-run Chinook salmon, Spring-run Chinook salmon, Central Valley Steelhead

## POPULATION STATUS

### Winter-run Chinook Salmon
#### Delta Life Stages
#### Brood Year 2021 Productivity

* Natural Winter-run Chinook salmon: **historical data number and estimate passed RBDD**
* Hatchery Winter-run Chinook salmon: 

### Spring-run Chinook Salmon
#### Delta Life Stages
#### Brood Year 2021 Productivity

* Natural Spring-run Chinook salmon: **historical data number**
* Hatchery Spring-run Chinook salmon: 
* Hatchery Spring-run Chinook salmon surrogates associated with the ITP
* San Joaquin River Restoration Program (SJRRP) Salmon Conservation and Research Facility (SCARP) Chinook salmon: 

### Central Valley Steelhead
#### Delta Life Stages
#### Brood Year 2021 Productivity

* Spawner abundance:
* Natural steelhead:
* Hatchery steelhead:

## DISTRIBUTION
### Winter-run Chinook Salmon
#### Current Distribution

* **info on percentage in Delta, exited Delta** 
* **info on natural loss**
* **info on hatchery loss**
* **info on flows at Mill and Deer creek**

#### Historic Trends

* **percent of winter-run Chinook salmon that should have been observed in salvage by this time of the water year (Table 3)**


#### Forecasted Distribution within Central Valley and Delta regions

* **info on entrainment tool estimates of median and maximum loss**
* **Genetic information from salvage**





### Spring-run Chinook Salmon
#### Current Distribution
* **percent of CV spring-run present in Delta (Table 1)**

#### Historical Trends
#### Forecasted Distribution within Central Valley and Delta Regions
* **percent of YOY spring-run observed in salvage by this time of the water year (Table 3)**
* **Deer Creek flows**





### Central Valley Steelhead
#### Current Distribution 
* **percent present in the Delta (Table 1)**
* **total hatchery loss**
* **total natural loss Dec-Mar**
* **combined natural loss Apr-June**

#### Historical Trends
* **historical trends percent steelhead in salvage**

#### Forecasted Distribution within Central Valley and Delta regions
* **percent present in Delta**
* **entrainment tool estimates (SacPAS)**


### TABLES

#### TABLE 1.Salmonid distribution estimates
https://www.cbr.washington.edu/sacramento/data/juv_monitoring.html
```{r, echo = FALSE}
# code for making table here (or pulling table from SacPAS)
```

#### TABLE 2. Historic migration and salvage patterns
```{r}

```

#### TABLE 3. STARS model output
```{r}

```


```{r CDECflows, echo = FALSE}
# Define parameters ----------------------------------
stations <-  c("MLM", "DCV", "WLK")
sta <- stations
start <- today() - 8
end <- today()
sensors <- c("20") # Flow event
interval <- "E" # Event = every 15 minutes, H = Hourly, A = Annual, D = Daily
# Download data, bind, write --------------------------------------------
Flow_data <- lapply(stations,
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensors,
                              dur_code = interval,
                              start_date = start,
                              end_date = end)
                 })
# Combine data and clean data ---------------------------------------------
Flow_df <- dplyr::bind_rows(Flow_data) %>%
  mutate(date = date(datetime)) %>%
  select(date, station = location_id, flow = parameter_value) %>%
  group_by(station, date) %>%
  summarize(meanFlow = mean(flow)) %>%
  ungroup()

Flow_wide <- Flow_df %>%
  pivot_wider(names_from = "station", values_from = "meanFlow") %>%
  mutate(MLM_change = (MLM - lag(MLM))/lag(MLM) * 100,
         DCV_change = (DCV - lag(DCV))/lag(DCV) * 100,
         WLK_change = (WLK - lag(WLK))/lag(WLK) * 100) %>%
  na.omit() %>%
  mutate(across(.cols = DCV:WLK_change, .fns = ~ round(.x, digits = 1))) %>%
  mutate(MLM_alert = "Flow>95cfs",
         DCV_alert = "Flow>95cfs") %>%
  select(MLM_flow = MLM, MLM_change, MLM_alert, 
         DCV_flow = DCV, DCV_change, DCV_alert,
         WLK_flow = WLK, WLK_change)
```

```{r, echo = FALSE}
flextable(Flow_wide) %>%
            set_caption("TABLE 4. Mean daily flow and percent change (Wilkins Slough, Deer Creek, Mill Creek; cfs from CDEC) and temperature and percent change (Knights Landing; °F from RST)") %>%
  vline()
```


#### TABLE 5. a) WY 2022 loss and salvage predictor data: Predicted weekly loss of winter-run Chinook salmon and steelhead at CVP and SWP facilities. b) Environmental details, current and forecast.

```{r}

```

#### TABLE 6. Preliminary survival (Φ) results for acoustically tagged salmonids (Chinook and steelhead). Individual studies denoted by rows with bold lines.
```{r}

```


### FIGURES

#### FIGURE 1.

#### FIGURE 2.

#### FIGURE 3.Predicted weekly loss of steelhead and winter-run Chinook salmon at the CVP and SWP facilities

```{r, echo = FALSE}
url <- "https://www.cbr.washington.edu/sacramento/data/graphics/juvloss_2_NONE.png"
```

![](`r url`)



## EVALUATION




### 1. 
### 2. 

### 3. What is the likelihood of increased loss exceeding the next annual loss threshold (50%, 75% or 90% of threshold) resulting in OMR management actions based on population distribution, abundance, and behavior of fish in the Delta?


**Calculate Loss**


*Also relevant to Table 2a in Outlook*

```{r, echo = FALSE}
# Read steelhead and salmon data

library(readr)
salmon_file = list.files(data_folder, pattern = "Salmon_2022_*", full.names = TRUE)
salmon_loss_data <- purrr::map(salmon_file, ~ read_csv(.x, col_types = cols(SampleDate = col_date(format = "%m/%d/%Y")))) %>%
  bind_rows()

steelhead_file = list.files(data_folder, pattern = "Steelhead_Salvage_Summary_2022_rawdata_*", full.names = TRUE)
steelhead_loss_data <- purrr::map(steelhead_file, ~ read_csv(.x, col_types = cols(Date = col_date(format = "%m/%d/%Y")))) %>%
  bind_rows() %>%
  mutate(month = month(Date),
         category = ifelse(month<4 | month>=8, "SH-early", "SH-late"))
```

```{r, echo = FALSE}
SH.loss <- steelhead_loss_data %>% 
  group_by(category) %>%
  summarise(loss_SWPN = sum(Loss_SWPN,na.rm = TRUE),
            loss_SWPC = sum(Loss_SWPC, na.rm = TRUE),
            loss_CVPN = sum(Loss_CVPN,na.rm = TRUE),
            loss_CVPC = sum(Loss_CVPC,na.rm = TRUE)) %>% 
  mutate(loss_natural= loss_SWPN + loss_CVPN,
         loss_clipped = loss_SWPC + loss_CVPC)

SH.loss.sub <- SH.loss %>%
  dplyr::select(species_race = category, 
         loss_unclipped = loss_natural,
         loss_clipped)

salmon.loss.all <- salmon_loss_data %>%  group_by(ADCLIP, `Size Race`) %>% summarise(loss_total = sum(LOSS))

salmon.loss.sub <- salmon.loss.all %>%
  pivot_wider(names_from = "ADCLIP", values_from = "loss_total") %>%
  rename(loss_unclipped =N,
         loss_clipped = C,
         species_race = `Size Race`)

loss <- rbind(SH.loss.sub, salmon.loss.sub)
```

```{r, echo = FALSE}
library(flextable)
flextable(loss) %>% 
  vline() %>%
  border_outer()
```


4. 
5. 

# Biology, Distribution, and Evaluation of Green Sturgeon
## POPULATION STATUS
## DISTRIBUTION
## EVALUATION
```{r}

```




# Biology, Distribution, and Evaluation of Delta Smelt

## DISTRIBUTION
```{r}

```

### Current Distribution

### Cultured Delta Smelt Experimental Releases

### Historical Trends

### Forecasted Distribution within Central Valley and Delta Regions


```{r Table 1}

```

```{r Table 2}

```

```{r Table 3}

```

```{r Table 4}

```

```{r Table 5}

```

# ABIOTIC CONDITIONS

## Turbidity
Use CDECRetrieve - SensorDownload.R 
Look at just data from the past week 
- Water temperature, Flow
- 3 day averages 

Download Data
```{r}

```


## X2 Conditions

## Other Environmental Conditions

# Evaluation

# Delta Smelt References