---
title: "Weekly Assessment of CVP and SWP Delta Operations on ESA-listed Species"
author: "Bureau of Reclamation"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(knitr)
library(tidyr)
library(readxl)
library(flextable)
library(xml2)
library(rvest)
library(CDECRetrieve)
```

```{r, echo = FALSE}
data_folder <- "data_report/"
```
## Chinook Salmon

### TABLES

#### TABLE 2. Historic migration and salvage patterns.Last updated `r format(Sys.time(), '%m/%d/%Y')`
```{r, echo = FALSE}


samt_url <- "https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html"
page <- read_html(samt_url)

tables <- page %>% 
  html_nodes("table") %>%
  html_table(fill = T) 

table_historic <- tables[[8]] %>%
  dplyr::bind_rows() %>%
  janitor::clean_names(case = "upper_camel")

table_historic <- data.frame(lapply(table_historic, function(x) {gsub("BY", " BY", x)})) 
table_historic <- data.frame(lapply(table_historic, function(x) {gsub("WY", " WY", x)})) 
```

```{r, echo = FALSE}
flextable(table_historic) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  bold(part = "header")
```

\newpage
#### TABLE 3. Mean daily flow and percent change (Wilkins Slough, Deer Creek, Mill Creek; cfs from CDEC) and temperature and percent change (Knights Landing; °F from RST)

```{r CDECflows, echo = FALSE, include = FALSE, eval = FALSE}
# Define parameters ----------------------------------
stations <-  c("MLM", "DCV", "WLK")
sta <- stations
start <- today() - 8
end <- today()
sensors <- c("20") # Flow event
interval <- "E" # Event = every 15 minutes, H = Hourly, A = Annual, D = Daily
# Download data, bind, write --------------------------------------------
Flow_data <- lapply(stations,
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensors,
                              dur_code = interval,
                              start_date = start,
                              end_date = end)
                 })
# Combine data and clean data ---------------------------------------------
Flow_df <- dplyr::bind_rows(Flow_data) %>%
  mutate(date = date(datetime)) %>%
  select(date, station = location_id, flow = parameter_value) %>%
  group_by(station, date) %>%
  summarize(meanFlow = mean(flow)) %>%
  ungroup()

Flow_wide <- Flow_df %>%
  pivot_wider(names_from = "station", values_from = "meanFlow") %>%
  mutate(`MLM change` = (MLM - lag(MLM))/lag(MLM) * 100,
         `DCV change` = (DCV - lag(DCV))/lag(DCV) * 100,
         `WLK change` = (WLK - lag(WLK))/lag(WLK) * 100) %>%
  na.omit() %>%
  mutate(across(.cols = DCV:`WLK change`, .fns = ~ round(.x, digits = 1))) %>%
  mutate(MLM_alert = ifelse(MLM > 95, "Yes", "No"),
         DCV_alert = ifelse(DCV > 95, "Yes", "No")) %>%
  select(Date = date,
         `MLM flow` = MLM, `MLM change`, `MLM alert` = MLM_alert, 
         `DCV flow` = DCV, `DCV change`, `DCV alert` = DCV_alert,
         `WLK flow` = WLK, `WLK change`)
```

```{r, echo = FALSE}
samt_url <- "https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html"
page <- read_html(samt_url)

tables <- page %>% 
  html_nodes("table") %>%
  html_table(fill = T) 

table_cdec <- tables[[6]] %>%
  dplyr::bind_rows() %>%
  rename(`Alert Triggered` = `WLK-KNL: Alert`)
```


```{r, echo = FALSE}
flextable(table_cdec) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = c(1, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8))%>%
  bold(part = "header")
```

\newpage
#### TABLE 4. STARS model simulations for route-specific entrainment, travel times, and survival. Travel time is calculated in days.

```{r, echo = FALSE}
samt_url <- "https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html"
page <- read_html(samt_url)

tables <- page %>% 
  html_nodes("table") %>%
  html_table(fill = T) 

table_stars <- tables[[11]] %>%
  dplyr::bind_rows() %>% mutate(Estimate=format(round(Estimate, 2), nsmall = 2))
```

```{r, echo = FALSE}
table_stars_w <- tidyr::pivot_wider(table_stars, names_from = "Parameter", values_from  = "Estimate", id_cols = c("Stock", "Date", "Route"))

flextable(table_stars_w) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  bold(part = "header")
```
\newpage
#### TABLE 5. a) WY 2022 loss and salvage predictor data: Predicted weekly loss of winter-run Chinook salmon and steelhead at CVP and SWP facilities. 

```{r, echo = FALSE}
samt_url <- "https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html"
page <- read_html(samt_url)

tables <- page %>% 
  html_nodes("table") %>%
  html_table(fill = T) 

table_environment <- tables[[9]] %>%
  dplyr::bind_rows()
table_predictor <- tables[[10]] %>%
  dplyr::bind_rows()
```

```{r, echo = FALSE}
table_predictor_w <- table_predictor %>%
  janitor::clean_names(case = "upper_camel") %>%
  mutate(Type = ifelse(grepl("Observed", ParameterDescription), "Observed", "Predicted")) %>%
  filter(Type == "Predicted",
         !grepl("Low", ParameterToken)) %>%
  pivot_wider(names_from = "Week", values_from = "Value", id_cols = c("ParameterToken", "ParameterDescription")) %>%
  select(-ParameterToken) 

colnames(table_predictor_w) <- c("Parameter", "Modeled Current Week", "Modeled Next Week")

flextable(table_predictor_w) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  autofit()%>%
  bold(part = "header")
  
```

#### TABLE 5. b) Environmental details, current and forecast.
```{r, echo = FALSE}
table_env_w <- table_environment %>%
  janitor::clean_names(case = "upper_camel") %>%
  pivot_wider(names_from = "WeekType", values_from = "Value", id_cols = c("ParameterToken", "ParameterDescription", "WaterYear")) %>%
  mutate(Parameter = case_when(ParameterToken == "temp.mal"  ~ "Temperature (Mallard Island, C)",
                               ParameterToken == "precip" ~ "Precipitation (5-d running sum, inches)",
                               ParameterToken == "om.sum" ~ "Old and Middle River Flows (cfs)",
                               ParameterToken == "sac" ~ "Sacramento River Flow (Freeport, cfs)",
                               ParameterToken == "dcc" ~ "DCC Gates",
                               ParameterToken == "sjr" ~ "San Joaquin River Flow (Vernalis, cfs)",
                               ParameterToken == "export" ~ "Export",
                               TRUE ~ "NA")) %>%
  filter(Parameter != "NA") %>%
  select(Parameter, Data, Forecast)

flextable(table_env_w) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  autofit()%>%
  bold(part = "header")

```
\newpage
### FIGURES

```{r, echo=FALSE}
# Define variable containing url
url_wr <- "https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2024/samt_lsp_winter.png"

url_steel <- "https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2024/samt_lsp_stlhd.png"

url_wr_loss_1 <- "https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2023/LossUnclip_1_currhist.png"
url_wr_loss_2 <- "https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2023/LossUnclip_1_Winter_spaghetti.png"

url_sth_loss_1 <- "https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2023/LossUnclip_2_currhist.png"

```

!["Winter Run Loss Plot"](`r url_wr`)
!["Steelhead Loss Plot"](`r url_steel`)

#### Figure 1. Predicted weekly loss of steelhead and winter-run Chinook salmon at the CVP and SWP facilities

!["Winter Run Cumulative Loss with Historical Loss Plot"](`r url_wr_loss_1`)
!["Winter Run Cumulative Loss with Historical Loss Plot (all WY plotted)"](`r url_wr_loss_2`)

#### Figure 2. Cumulative natural winter-run Chinook salmon loss for the year (blue) and 2009 – 2018 historic cumulative loss (gray, different symbols). Historic daily mean plotted in black circles

!["Steelhead Cumulative Loss"](`r url_sth_loss_1`)

#### Figure 3. Cumulative natural steelhead loss for the year (blue) and 2009 – 2018 historic cumulative loss (gray). Historic daily mean plotted in black circles.  

