---
title: "Weekly Assessment of CVP and SWP Delta Operations on ESA-listed Species"
author: "Bureau of Reclamation"
date: '2022-08-09'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
```

# Executive Summary

# Operational and Regulatory Conditions

# Biology, Distribution, and Evaluation Winter-run Chinook salmon, Spring-run Chinook salmon, Central Valley Steelhead

## POPULATION STATUS
### Winter-run Chinook Salmon
#### Delta Life Stages
#### Brood Year 2021 Productivity

### Spring-run Chinook Salmon
#### Delta Life Stages
#### Brood Year 2021 Productivity

### Central Valley Steelhead
#### Delta Life Stages
#### Brood Year 2021 Productivity

## DISTRIBUTION
### Winter-run Chinook Salmon
### Spring-run Chinook Salmon
### Central Valley Steelhead


## EVALUATION

### 1. 
### 2. 

### 3. What is the likelihood of increased loss exceeding the next annual loss threshold (50%, 75% or 90% of threshold) resulting in OMR management actions based on population distribution, abundance, and behavior of fish in the Delta?


**Calculate Loss**
"SAMTsummary.R"

*Also relevant to Table 2a in Outlook*


Read steelhead table, read salmon table
```{r}

```


Produce a Table: 

Species/Race | Unclipped | Clipped
Winter Run
Spring Run
Steelhead Dec-Mar
Steelhead Apr-Jun
```{r}

```


4. 
5. 






# Biology, Distribution, and Evaluation of Delta Smelt

## Distribution
```{r}

```

### Current Distribution

### Cultured Delta Smelt Experimental Releases

### Historical Trends

### Forecasted Distribution within Central Valley and Delta Regions


```{r Table 1}

```

```{r Table 2}

```

```{r Table 3}

```

```{r Table 4}

```

```{r Table 5}

```

# ABIOTIC CONDITIONS

## Turbidity
Use CDECRetrieve - SensorDownload.R 
Look at just data from the past week 
- Water temperature, Flow
- 3 day averages 

Download Data
```{r}

```


## X2 Conditions

## Other Environmental Conditions

# Evaluation

# Delta Smelt References